---
title: "Available Palettes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{available-palettes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Install from CRAN using:
``` {r, eval = FALSE}
install.packages("PrettyCols")
```

Or install the development version using:
``` {r, eval = FALSE}
remotes::install_github("nrennie/PrettyCols")
```

Then load into R:
```{r}
library(PrettyCols)
```

## Sequential Palettes

### Blues
```{r, out.width = "60%", fig.align="center"}
prettycols("Blues")
```

### Purples
```{r, out.width = "60%", fig.align="center"}
prettycols("Purples")
```

### Tangerines
```{r, out.width = "60%", fig.align="center"}
prettycols("Tangerines")
```

### Greens
```{r, out.width = "60%", fig.align="center"}
prettycols("Greens")
```

### Pinks
```{r, out.width = "60%", fig.align="center"}
prettycols("Pinks")
```

### Teals
```{r, out.width = "60%", fig.align="center"}
prettycols("Teals")
```

### Yellows
```{r, out.width = "60%", fig.align="center"}
prettycols("Yellows")
```

### Reds
```{r, out.width = "60%", fig.align="center"}
prettycols("Reds")
```

## Diverging Palettes

### PurpleGreens
```{r, out.width = "60%", fig.align="center"}
prettycols("PurpleGreens")
```

### PinkGreens
```{r, out.width = "60%", fig.align="center"}
prettycols("PinkGreens")
```

### TangerineBlues
```{r, out.width = "60%", fig.align="center"}
prettycols("TangerineBlues")
```

### PurpleGreens
```{r, out.width = "60%", fig.align="center"}
prettycols("PurpleGreens")
```

### PurplePinks
```{r, out.width = "60%", fig.align="center"}
prettycols("PurplePinks")
```

### TealGreens
```{r, out.width = "60%", fig.align="center"}
prettycols("TealGreens")
```

### PurpleYellows
```{r, out.width = "60%", fig.align="center"}
prettycols("PurpleYellows")
```

### RedBlues
```{r, out.width = "60%", fig.align="center"}
prettycols("RedBlues")
```

## Qualitative Palettes

### Bold
```{r, out.width = "60%", fig.align="center"}
prettycols("Bold")
```

### Light
```{r, out.width = "60%", fig.align="center"}
prettycols("Light")
```

### Dark
```{r, out.width = "60%", fig.align="center"}
prettycols("Dark")
```

### Neon
```{r, out.width = "60%", fig.align="center"}
prettycols("Neon")
```

### Summer
```{r, out.width = "60%", fig.align="center"}
prettycols("Summer")
```

### Autumn
```{r, out.width = "60%", fig.align="center"}
prettycols("Autumn")
```

### Winter
```{r, out.width = "60%", fig.align="center"}
prettycols("Winter")
```

### Rainbow
```{r, out.width = "60%", fig.align="center"}
prettycols("Rainbow")
```

### Beach
```{r, out.width = "60%", fig.align="center"}
prettycols("Beach")
```

### Fun
```{r, out.width = "60%", fig.align="center"}
prettycols("Fun")
```

### Sea
```{r, out.width = "60%", fig.align="center"}
prettycols("Sea")
```

### Bright
```{r, out.width = "60%", fig.align="center"}
prettycols("Bright")
```

### Relax
```{r, out.width = "60%", fig.align="center"}
prettycols("Relax")
```

### Lucent
```{r, out.width = "60%", fig.align="center"}
prettycols("Lucent")
```

### Lively
```{r, out.width = "60%", fig.align="center"}
prettycols("Lively")
```

### Joyful
```{r, out.width = "60%", fig.align="center"}
prettycols("Joyful")
```
