---
title: "Colourblind Friendly Palettes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{colourblind-friendly-palettes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Install from CRAN using:
``` {r, eval = FALSE}
install.packages("PrettyCols")
```

Or install the development version using:
``` {r, eval = FALSE}
remotes::install_github("nrennie/PrettyCols")
```

Then load into R:
```{r}
library(PrettyCols)
```

To return a data frame of which colour palettes are colourblind friendly, use:
```{r, eval = F}
colourblind_friendly()
```
Note that the `colorblind_friendly()` is the same function.

To view the palettes that are colourblind friendly, set the `colourblind_friendly` argument in `view_all_palettes()` to `TRUE`. To view all colourblind friendly palettes:

```{r, out.width = "60%", fig.align="center"}
view_all_palettes(colourblind_friendly = TRUE)
```

This can be combined with a palette type. For example, to view all diverging colour palettes that are colourblind friendly:
```{r, out.width = "60%", fig.align="center"}
view_all_palettes(type = "div", colourblind_friendly = TRUE)
```

Colourblind friendliness was checked using the {colorblindcheck} R package.





